Intrusion Detection with \\ Genetic Algorithms and Fuzzy Logic

### 2013-12-06 Talk/Presentation.tex
Added more to the big picture slide.

\begin{frame}
  \frametitle{The Big Picture}
  \begin{itemize}
  	\item Computer lab gets large numbers of login attempts that are attempts at intrusion.
	\begin{itemize}
		\item Trying to gain root access to the system
		%\item Delete files of users and change user passwords.
	\end{itemize}
	\linespace
	\item With intrusion detection system (IDS): classify attempts.
	\item Intrusion detection systems provide a way of detecting attacks by monitoring network activities for malicious or abnormal behaviors then producing reports, alerts, actions.
	\item Training an IDS: use a fuzzy genetic algorithm.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{The Big Picture}
  \begin{itemize}
  	\item Computer lab gets large numbers of login attempts that are attempts at intrusion.
	\begin{itemize}
		\item Trying to gain root access to the system
		\item Delete files of users and change user passwords.
	\end{itemize}
	\linespace
	\linespace
	\linespace

	\item An attempt is an attack if there are more than \emph{n} number of attempts within \emph{t} time interval.
	\item Number of login attempts (for failed passwords or for users that don't exist) over period of 6 days (12/1 - 12/6):
	\begin{itemize}
		\item normal lab box (avenger): 1,834 attacks
		\item normal box, more recently added than avenger (kenshiro): 1,887 attacks
	\end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Big Picture}
  \begin{itemize}
	\item With intrusion detection system (IDS): classify attempts.
	\item Intrusion detection systems provide a way of detecting attacks by monitoring network activities for malicious or abnormal behaviors then producing reports, alerts, actions.
	\item Training an IDS: use a fuzzy genetic algorithm.
  \end{itemize}
\end{frame}
